\documentclass[a4paper]{article}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[left=3cm, right=3cm, top=2cm]{geometry}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\hypersetup{citecolor=green} 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}


\title{Project Scope and Timeline}
\author{Pranav Sankhe \\ Indian Institute of Technology, Bombay}
\date{\today}

\begin{document}

\maketitle


\section*{Project's scope}

From August 2019 to July 2020 I will be working on my Master's Thesis project. I will be graduating with a Bachelor's and Master's degree in August 2020.
I intend to work in the field of auditory perception and I wish my master's thesis project to be based on the same. The project which I will be working on at CCRMA will continue as my master's thesis project at my university. \\

What I want to accomplish at CCRMA is, to start the project, discuss and set the problem statement and get some preliminary results in the span of 2 months or so. Also I want to establish a good rapport between my advisor at CCRMA during my stay which will further ensure easy communication for the online collaboration when I return back to India and work on the same project. \\ 

This depends heavily on the time span for which I will be at CCRMA. I am also donw to work on a mini project at CCRMA which will give me a good research heads-up for my master's thesis work.


\section*{Project's timeline}
A rough sketch of my project timeline is as follows:
\begin{itemize}
\item First two weeks: Decide the exact problem statement, scope of the project, what datasets I will be using for analysis and literature review 
\item 4 weeks: Work towards implementing what has been decided
\item Last two weeks: Get the results and discuss the interpretations. Also, plan out the future work given the results achieved.    
\end{itemize}



\end{document}  
